Solving GENOPT problems \newline with the use of ExaMin solver

### 2016-07-20 2016/LION10/GenOpt.tex
Финальная версия статьи ни LION, которую я выложил (по просьбе оргкомитета конференции) в EasyChair

\begin{figure}
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1a.jpg} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1b.jpg} \\ (b)}
\end{minipage}
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1c.jpg} \\ (c)}
\end{minipage}
\caption{Evolvents in two dimensions with (a) $m=3$, (b) $m=4$ and (c) $m=5$}
\label{fig:0}
\end{figure}

@@

	\begin{itemize}
		\item To perform the GSA iterations until the current optimum (the minimal value of the objective function in the trial points computed already) is renovated.
	\end{itemize}

>>>>

\begin{figure}
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1a.JPG} \\ (a)}
\end{minipage}
\hfill
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1b.JPG} \\ (b)}
\end{minipage}
\begin{minipage}{0.32\linewidth}
\center{\includegraphics[width=1.0\linewidth]{fig1c.JPG} \\ (c)}
\end{minipage}
\caption{Evolvents in two dimensions with (a) $m=3$, (b) $m=4$ and (c) $m=5$}
\label{fig:0}
\end{figure}

@@

	\begin{itemize}
		\item Perform the GSA iterations until the current optimum (the minimal value of the objective function in the trial points computed already) is renovated.
	\end{itemize}
